---
title: "Beelzebulb's Logic Code"
output: html_notebook
---

# Libraries that will be required
```{r}
library(tidyverse)
library(DBI)
library(rsconnect)
```

# AWS Connection
```{r}
getAWSConnection <- function(){
  conn <- dbConnect(
    drv = RMySQL::MySQL(),
    dbname = "student055",
    host = "esddbinstance-1.ceo4ehzjeeg0.ap-southeast-1.rds.amazonaws.com",
    username = "student055",
    password = "gVU4KpWT")
  conn
}
```


# Cards of A Deck Logic

## Generating the deck of cards dataframe
```{r}
cardID_deck <- rep(c(1001, 1002, 1003, 1004), each = 5)
cardNAME_deck <- rep(c("Wire_1", "Wire_2", "Wire_3", "Wire_4"), each = 5)
df_id <- data.frame(Card_ID = cardID_deck, Card_Name = cardNAME_deck)

df_id2 <- data.frame(Card_ID = rep(c(2001, 2002, 2003, 2004), each = 5), Card_Name = rep(c("Wire_Left", "Wire_Right", "Wire_Up", "Wire_Down"), each = 5))
# df_id2
```
## Sending Fresh Deck of Cards to Database (For Every new Game)
```{r}
# querytemplate <- "INSERT INTO CardDeck (Card_ID, Card_Name) VALUES"
# sql_qry <- paste0(querytemplate, paste(sprintf("('%s', '%s')", as.numeric(df_id$Card_ID), df_id$Card_Name), collapse = ","))
# print(sql_qry)
# conn <- getAWSConnection()
# # query<- sqlInterpolate(conn, sql_qry)
# result <- dbExecute(conn, sql_qry)
# result

## TRY THIS
# If Dataframe or Table == df_id:
conn <- getAWSConnection()
dbWriteTable(conn, "CardDeck", df_id, overwrite = TRUE)
```

## Drawing a sample from the deck

```{r}
conn <- getAWSConnection()
query_draw_cards <- dbGetQuery(conn, "SELECT row_names, Card_ID, Card_Name FROM CardDeck ORDER BY RAND() LIMIT 5")
dbDisconnect(conn)
query_draw_cards
```
## Assigning the Cards to the Player
```{r}
conn <- getAWSConnection()
playerid <- 3
query_draw_cards["PlayerID"] <- playerid
query_draw_cards
querytemplate_drawcards <- "INSERT INTO HandCards (PlayerID, Card_ID, Card_Name) VALUES"
sql_qry <- paste0(querytemplate_drawcards, paste(sprintf("(%d, %d, '%s')",
as.numeric(query_draw_cards$PlayerID),
as.numeric(query_draw_cards$Card_ID),
query_draw_cards$Card_Name), collapse = ","))
sql_qry
send_query <- dbExecute(conn, sql_qry)
# send_query
dbDisconnect(conn)
```


## Removing the sample drawn from the deck

```{r}
conn <- getAWSConnection()
for(i in 1:nrow(query_draw_cards)){
  remove_template <- "DELETE FROM CardDeck where row_names = ?row"
  qrc <- sqlInterpolate(conn, remove_template, row = query_draw_cards[i, 1])
  print(qrc)
  query_remove_card <- dbExecute(conn, qrc)
}
dbDisconnect(conn)
```


## Clearing the database of any other cards still in it (Working)
```{r}
# use   truncate tableName;
# Truncate: will also delete the rows from your table but it will start from new row with 1.
qry_truncate <- "TRUNCATE CardDeck"
exec_trunctate <- dbExecute(conn, qry_truncate)
```

# Placing of Cards on the board

## Obtaining the grid cells for the board

## Placing an image that will represent the board

## Opening a module for any of the cell that is clicked.

## Retrieving from database the cards that the current player_id has.

## Dropdown box to select the card and press confirm

## Show the card on the board.




# Physics Questions

## Adding of Data to the databases
```{r}
mcq <- 4
qns <- 10
mcq_choices <- function(qns, mcq){
  ch <- c()
  print(ch)
  for(i in 1:qns){
    for(j in 1:mcq){
      ch <- c(ch, paste("This is qn", i, "and here is the choice", j))
    }
  }
  return(ch)
}

physicsans <- data.frame(qn_id = rep(c(1:10), each = mcq),
                          ans_id = c(1:(qns*mcq)),
                          choice = mcq_choices(qns, mcq))
physicsans
  
conn <- getAWSConnection()
dbWriteTable(conn, "PhysicsAns", physicsans, overwrite = TRUE)
```


## Retrieving Random Physics Question from the database

```{r}
conn <- getAWSConnection()
physics_qn_id <- 1
query_pn_template <- "SELECT question, ans_id FROM PhysicsQn WHERE qn_id = ?qn_id"
query_physics_question <- sqlInterpolate(conn, query_pn_template, qn_id = physics_qn_id)
exec_query_pq <- dbGetQuery(conn, query_physics_question)
dbDisconnect(conn)
exec_query_pq
```


## Retrieving Random Phyiscs Question Answer Choices from the database

```{r}
conn <- getAWSConnection()
physics_qn_id <- 1
query_pc_template <- "SELECT ans_ID, choice FROM PhysicsAns WHERE qn_id = ?qn_id"
query_physics_choices <- sqlInterpolate(conn, query_pc_template, qn_id = physics_qn_id)
exec_query_pc <- dbGetQuery(conn, query_physics_choices)
dbDisconnect(conn)
exec_query_pc
```


## Displaying Question and Choices on a module screen (with drop down and confirm button or Radio Button)

## Checking if the answer given is the same as the correct answer ID in the database for that question

## Module Response to show whether correct or wrong.

## Consequence of Right / Wrong answer.

# Checking for Defeat Condition
```{r}
query_cards_result <- dbGetQuery(conn,"SELECT Card_ID FROM CardDeck")
query_cards_result

if (nrow(query_cards_result) == 0){
  print("Zero rows returned, Defeat Condition Reached")
}

dbDisconnect(conn)
```


```{r}

x = 5
y = x %% 4
print(y)
```

